\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{xcolor}

\pagestyle{fancy}
\lhead{Study Contract}
\rhead{Page \thepage\ of \pageref{LastPage}}
\cfoot{}

\title{\textbf{STUDY COMMITMENT AND BEVERAGE PROCUREMENT CONTRACT}}
\author{}
\date{}

\begin{document}

\maketitle

\section*{PARTIES TO THIS AGREEMENT}

This contract is entered into as of the date of signature below, between:

\begin{enumerate}[label=\arabic*.]
    \item \textbf{Oliver Form} (hereinafter referred to as ``Party A''), and
    \item \textbf{Leo Williams} (hereinafter referred to as ``Party B'')
\end{enumerate}

Collectively referred to as the ``Parties'' or the ``Agreement.''

\section*{RECITALS}

WHEREAS, the Parties acknowledge their mutual commitment to academic excellence in preparation for A-Level Mathematics and Further Mathematics examinations; and

WHEREAS, the Parties recognize that consistent practice through past papers is essential to examination success; and

WHEREAS, the Parties desire to establish a binding mutual accountability mechanism with enforceable consequences;

NOW, THEREFORE, in consideration of the mutual covenants and agreements contained herein, the Parties agree as follows:

\section*{DEFINITIONS}

\begin{enumerate}[label=\arabic*.]
    \item \textbf{``Past Papers''} shall mean formally published examination papers from official examination boards (AQA, Edexcel, OCR, or Pearson) for A-Level Mathematics and/or A-Level Further Mathematics.
    
    \item \textbf{``Week''} shall mean any calendar week from Monday 00:00 through Sunday 23:59 (GMT/BST).
    
    \item \textbf{``Complete''} shall mean fully attempting all questions on the past paper, with written solutions for all questions attempted. Completion must occur on or before 23:59 on Sunday of the relevant week.
    
    \item \textbf{``Exam Period''} shall mean from the date of signature of this contract through the final scheduled A-Level examination in Mathematics or Further Mathematics, whichever is latest.
    
    \item \textbf{``Alcoholic Beverage''} shall mean any drink of the Recipient's choice, purchased from a licensed establishment, with a maximum unit cost of £8.00 GBP per beverage.
\end{enumerate}

\section*{CORE OBLIGATIONS}

\subsection*{Weekly Completion Requirement}

Each Party agrees to complete a minimum of two (2) full past papers per week during the Exam Period, as defined above.

\begin{enumerate}[label=\alph*.]
    \item Papers may be from any available year or examination board.
    \item Papers may be combined from Mathematics and Further Mathematics.
    \item Digital completion (typed or photographed solutions) is acceptable.
    \item Papers must be completed by 23:59 on the final Sunday of each week.
\end{enumerate}

\subsection*{Verification and Documentation}

\begin{enumerate}[label=\alph*.]
    \item Each Party shall maintain contemporaneous photographic or digital evidence of completed papers.
    \item Evidence must be provided within 48 hours of request.
    \item Failure to provide evidence within 48 hours shall be deemed as non-completion.
    \item Acceptable evidence includes: photographs of written work, scanned documents, or digital submissions with timestamps.
\end{enumerate}

\section*{ENFORCEMENT AND PENALTIES}

\subsection*{Default Definition}

A Party shall be in breach of this contract if they fail to complete two (2) past papers in any given week during the Exam Period.

\subsection*{Consequence of Default}

Upon verified breach of the weekly completion requirement:

\begin{enumerate}[label=\arabic*.]
    \item The breaching Party (``Debtor'') shall purchase one (1) alcoholic beverage for the non-breaching Party (``Creditor'') on the following Friday.
    
    \item If breach occurs in multiple weeks, the Debtor shall owe one (1) beverage per breached week, cumulative.
    
    \item Beverages must be purchased and consumed on the same Friday in which the debt is incurred, or within seven (7) days thereof.
    
    \item If multiple claims accumulate, the Debtor may satisfy all claims in a single occasion by purchasing the requisite number of beverages.
    
    \item The Creditor may elect the establishment and specific beverage, with the £8.00 maximum per unit.
\end{enumerate}

\section*{EXCEPTIONAL CIRCUMSTANCES}

\subsection*{Valid Exemptions}

A Party may be excused from the weekly requirement upon the occurrence of one or more of the following:

\begin{enumerate}[label=\arabic*.]
    \item \textbf{Illness:} Medically diagnosed illness preventing study, with supporting documentation (doctor's note, prescription receipt, etc.).
    
    \item \textbf{Examination Conflicts:} Scheduled official examinations during the week, reducing reasonable study capacity.
    
    \item \textbf{Family Emergency:} Death, hospitalization, or emergency requiring immediate family attention.
    
    \item \textbf{Hardware Failure:} Documented failure of essential equipment (computer, printer) preventing work submission, provided repair/replacement was initiated immediately.
    
    \item \textbf{Mutual Agreement:} Both Parties may mutually agree to waive a single week upon written consent via text message, email, or in-person agreement, documented by the Creditor.
\end{enumerate}

\subsection*{Exemption Procedure}

\begin{enumerate}[label=\alph*.]
    \item The claiming Party must notify the other Party within 48 hours of the exemption event.
    \item Supporting documentation must be provided within one (1) week of the exemption event.
    \item The Creditor may challenge an exemption claim; disputes shall be resolved per Section 8.
\end{enumerate}

\section*{DISPUTE RESOLUTION}

\subsection*{Good Faith Discussion}

Should any dispute arise regarding:
\begin{enumerate}[label=\arabic*.]
    \item Whether papers were properly completed
    \item Whether evidence is sufficient
    \item Whether an exemption was valid
    \item Any other interpretation of this contract
\end{enumerate}

The Parties shall first attempt resolution through good faith discussion within 48 hours of the dispute arising.

\subsection*{Mediation}

If discussion fails, the Parties shall refer the matter to a mutually agreed neutral third party (suggested: a trusted friend or teacher), who shall render a binding determination within 7 days.

\subsection*{Binding Nature of Determination}

The determination of the mediator shall be final and binding on both Parties. Non-compliance with the mediator's determination constitutes a material breach of this contract.

\section*{MODIFICATION AND TERMINATION}

\subsection*{Amendments}

This contract may only be modified by mutual written agreement of both Parties, documented via email or in-person signature.

\subsection*{Early Termination}

Should either Party's exams be cancelled or rescheduled, this contract shall terminate on the date of the last scheduled examination. Either Party may not unilaterally terminate this contract without the consent of the other Party.

\section*{GENERAL PROVISIONS}

\subsection*{Governing Law}

This contract shall be governed by the laws of the United Kingdom and the principles of good sportsmanship between friends.

\subsection*{Severability}

Should any provision be deemed unenforceable, the remaining provisions shall remain in full force and effect.

\subsection*{Entire Agreement}

This document constitutes the entire agreement between the Parties regarding the subject matter hereof and supersedes all prior negotiations and understandings.

\subsection*{Good Faith}

Both Parties agree to perform all obligations hereunder in good faith and fair dealing.

\section*{SIGNATURES AND ACKNOWLEDGMENT}

By signing below, each Party acknowledges that:
\begin{enumerate}[label=\arabic*.]
    \item They have read and understood the entire contract
    \item They agree to be bound by all terms and conditions
    \item They voluntarily enter into this agreement
    \item They understand that breach will result in the specified consequences
    \item They commit to good faith compliance and dispute resolution
\end{enumerate}

\vspace{2cm}

\noindent
\textbf{PARTY A:} \underline{\phantom{XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX}} 

Oliver Form

\vspace{0.5cm}
\noindent
Date: \underline{\phantom{XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX}}

\vspace{2cm}

\noindent
\textbf{PARTY B:} \underline{\phantom{XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX}}

Leo Williams

\vspace{0.5cm}
\noindent
Date: \underline{\phantom{XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX}}

\vspace{2cm}

\noindent
\textbf{WITNESS (OPTIONAL):} \underline{\phantom{XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX}}

Name (Print): \underline{\phantom{XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX}}

\vspace{0.5cm}
\noindent
Date: \underline{\phantom{XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX}}

\end{document}
